UniScatter: Unifying\\Backscatter Communications, Symbiotic Radio and Reconfigurable Intelligent Surface

### 2022-08-22 main.tex
:pencil: Discuss input distribution vs link priority

		As shown in Fig. \subref*{fi:block_diagram}, UniScatter nodes can be implemented over readily available passive backscatter devices with energy harvester and information decoder.
		Its equivalent circuit and scatter model are presented in Fig. \subref*{fi:equivalent_circuit} and \subref*{fi:scatter_model}.
		When activated by primary transmitter, each node harvests a proportion of the impinging wave for its own operation, decode the embedded coordination information for input distribution control, then applies a potentially random phase shift on the reradiated signal due to backscatter modulation.
		Energy harvesting and information decoding at passive UniScatter nodes can be realized using conventional power-splitting or time-sharing \gls{swipt} protocols \cite{Clerckx2019} or integrated energy-information receiver with pulse position modulated signal \cite{Kim2021a}.
		Besides, relevant \gls{csi} can be acquired using either traditional sequential methods \cite{Bharadia2015,Yang2015b,Guo2019g} or the state-of-the-art parallel approach \cite{Jin2021a}.
		In the following context, we assume perfect primary-backscatter coordination and perfect channel estimation for all links.
		\begin{figure*}[!t]
			\centering
			\subfloat[Block Diagram]{
				\resizebox{0.32\linewidth}{!}{
					\input{assets/illustration/block_diagram.tex}
				}
				\label{fi:block_diagram}
			}
			\subfloat[Equivalent Circuit]{
				\resizebox{0.37\linewidth}{!}{
					\input{assets/illustration/equivalent_circuit.tex}
				}
				\label{fi:equivalent_circuit}
			}
			\subfloat[Scatter Model]{
				\resizebox{0.28\linewidth}{!}{
					\input{assets/illustration/scatter_model.tex}
				}
				\label{fi:scatter_model}
			}
			\caption{Block diagram, equivalent circuit, and scatter model of a UniScatter node. The solid and dashed vectors represent signal and energy flows. The scattering antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
			\label{fi:uniscatter_node}
		\end{figure*}
	\end{subsection}

@@

			\mathcal{R}_{l} \triangleq [t_{l-1},t_l), \quad t_{l-1} \le t_l.

@@

\begin{section}{Rate-Region Characterization}
	To characterize the achievable primary-total-backscatter rate region of the proposed UniScatter system, we aim to maximize the weighted sum mutual information with respect to input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming $\boldsymbol{w}$, and decision thresholds $\boldsymbol{t}$ as
	\begin{maxi!}
		{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{w},\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
		\addConstraint{\boldsymbol{1}^T \boldsymbol{p}_k}{=1,}{\quad \forall k}{\label{co:sum_probability}}
		\addConstraint{\boldsymbol{p}_k}{\ge \boldsymbol{0},}{\quad \forall k}{\label{co:nonnegative_probability}}
		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P}{\label{co:transmit_power}}
		% \addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l.}{\label{co:decision_threshold}}
		\addConstraint{\boldsymbol{t}}{\ge \boldsymbol{0}.}{\label{co:decision_threshold}}
	\end{maxi!}
	Since problem \eqref{op:weighted_sum_rate} is highly non-convex, we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$ until convergence.

	\begin{subsection}{Input Distribution}
		For any given $\boldsymbol{w}$ and $\boldsymbol{t}$, we can construct the equivalent \gls{dmtmac} by \eqref{eq:dmtmac} and simplify \eqref{op:weighted_sum_rate} to
		\begin{maxi!}
			{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}}}{I(x_{\mathcal{K}})}{\label{op:input_distribution}}{}
			\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
		\end{maxi!}
		which involves the coupled term $\prod_{k \in \mathcal{K}} P_k(x_{m_k})$ and is non-convex when $K > 1$.
		Following \cite{Rezaeian2004}, we first recast \gls{kkt} conditions of problem \eqref{op:input_distribution} to their equivalent forms, then propose a numerical method that guarantees those conditions on convergence of sequences.
		% ? Next, we propose a numerical method that evaluate the \gls{kkt} input distribution by limit of sequences.
		\begin{remark}
			As demonstrated in \cite{Buhler2011}, \gls{kkt} conditions are generally necessary but insufficient for total rate maximization problems.
			Although \gls{kkt} solutions to problem \eqref{op:input_distribution} may end up being saddle points, we will later show by simulation their average performance can be reasonably close to optimal for a moderate $K$.
		\end{remark}
		\begin{proposition}
			The \gls{kkt} optimality conditions for problem \eqref{op:input_distribution} are equivalent to, $\forall k,m_k$,
			\begin{subequations}
				\label{eq:input_kkt_condition}
				\begin{alignat}{2}
					I_k^\star(x_{m_k}) & = I^\star(x_{\mathcal{K}}), \quad   &  & P_k^\star(x_{m_k}) > 0,\label{eq:probable_states} \\
					I_k^\star(x_{m_k}) & \le I^\star(x_{\mathcal{K}}), \quad &  & P_k^\star(x_{m_k}) = 0.\label{eq:dropped_states}
				\end{alignat}
			\end{subequations}
			\label{pr:input_kkt_condition}
		\end{proposition}

@@

	\begin{subsection}{Decision Threshold}
		For any given $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$ and $\boldsymbol{w}$, problem \eqref{op:weighted_sum_rate} reduces to
		\begin{maxi!}
			{\scriptstyle{\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:decision_threshold}}{\label{ob:decision_threshold}}
			\addConstraint{\eqref{co:decision_threshold},}
		\end{maxi!}
		which is still non-convex because variable $\boldsymbol{t}$ appears on the limits of integration \eqref{eq:dmtmac}.
		Fortunately, we can further simplify problem \eqref{op:decision_threshold} as a point-to-point rate-optimal quantizer optimization for a discrete-input continuous-output memoryless channel, thanks to Remark \ref{re:backscatter_decision} and \ref{re:augmented_source}.

@@

		Next, we constrain the feasible domain of problem \eqref{op:decision_threshold} from continuous space $\mathbb{R}_+^{L+1}$ to finite candidate set (i.e., fine-grained discrete energy levels) $\mathcal{T}^{L+1}$.
		\begin{figure}[!t]
			\centering
			\resizebox{0.9\columnwidth}{!}{
				\input{assets/illustration/discrete_outputs.tex}
			}
			\caption{
				The decision thresholds are selected from fine-grained discrete energy levels instead of continuous space, and each decision region consists of at least one neighbor energy bins.
			}
			\label{fi:discrete_outputs}
		\end{figure}
		As shown in Fig. \ref{fi:discrete_outputs}, by introducing the extra analog-to-digital conversion step, we can group adjacent high-resolution energy bins for backscatter decision regions.
		Thus, problem \eqref{op:decision_threshold} is recast as
		\begin{maxi}
			{\scriptstyle{\boldsymbol{t} \in \mathcal{T}^{L+1}}}{I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),}{\label{op:decision_threshold_recast}}{}
		\end{maxi}
		which can be solved by existing rate-optimal \gls{dmc} quantizer designs.
		For global optimal solutions, \cite{He2021} proposed a \gls{dp} method accelerated by the \gls{smawk} algorithm with computational complexity $\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T})-L)\bigr)$, and \cite{Nguyen2020a} presented a traverse-then-bisect algorithm using the optimality condition of three neighbor thresholds with complexity $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$.
		In Section \ref{se:simulation_results}, both schemes will be compared with the \gls{ml} thresholding scheme \cite{Qian2019}
		\begin{equation}
			t_{l}^{\mathrm{\gls{ml}}} = N \frac{\sigma_{l-1}^2 \sigma_{l}^2}{\sigma_{l-1}^2 - \sigma_{l}^2} \log \frac{\sigma_{l-1}^2}{\sigma_{l}^2}, \quad l \in \mathcal{L} \setminus \{L\},
			\label{eq:detection_threshold_maximum_likelihood}
		\end{equation}
		which is generally suboptimal for problem \eqref{op:decision_threshold} except when all nodes are with equiprobable inputs.
	\end{subsection}
\end{section}

\begin{section}{Simulation Results}
	% TODO compare PGD and primary-MRT beamformers
	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision design for the UniScatter system in Fig. \ref{fi:uniscatter_network}.
	We assume the AP-user distance is \qty{10}{\meter}, $K=2$ UniScatter nodes are randomly dropped within a disk of radius \qty{2}{\meter} centered at the user, the \gls{ap} is with $Q=4$ transmit antennas and an average power budget $P=\qty{36}{\dBm}$, the nodes employs \num{4}-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$, and the symbol period ratio is $N=20$.
	For all channels involved, we consider a distance-dependent path loss model
	\begin{equation}
		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma,
	\end{equation}
	together with a Ricean fading model
	\begin{equation}
		\boldsymbol{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\boldsymbol{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\boldsymbol{H}}
	\end{equation}
	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at distance $d_0=\qty{1}{\meter}$, $\kappa$ is the Ricean $K$-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with entries in standard \gls{iid} \gls{cscg} distribution.
	We choose $\gamma_{\mathrm{D}}=2.6$, $\gamma_{\mathrm{F}}=2.4$, $\gamma_{\mathrm{B}}=2$, and $\kappa_{\mathrm{D}}=\kappa_{\mathrm{F}}=\kappa_{\mathrm{B}}=5$ for direct, forward and backward links.
	The finite threshold domain $\mathcal{T}$ comes from $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence level $1-\varepsilon$, where $b=8$ and $\varepsilon=\num{2.22e-16}$.
	All achievable rate regions are averaged over \num{3000} realizations, and the parameters remain fixed unless otherwise specified.

	\begin{subsection}{Input Distribution vs. Weight}
		\begin{figure}[!t]
			\centering
			\subfloat[Instance 1\label{fi:distribution_weights_1}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/distribution_weights_1.tex}
				}
			}
			\subfloat[Instance 2\label{fi:distribution_weights_2}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/distribution_weights_2.tex}
				}
			}
			\caption{Typical input distributions vs. weight $\rho$ for a UniScatter node with $M=4$ inputs.}
			\label{fi:distribution_weights}
		\end{figure}
		% We consider a single UniScatter with $M=4$ inputs in this case of study.
		In Fig. \ref{fi:distribution_weights}, we present typical input distributions of a single UniScatter node with $M=4$ inputs under different weight $\rho$.
		Fig. \subref*{fi:distribution_weights_1} and \subref*{fi:distribution_weights_2} are obtained from \gls{iid} drop and channel realizations.
		We note that even for $\rho=0$ (i.e., best backscatter performance), the optimal input distribution is not equiprobable like \gls{sr}, and adaptive channel coding can further increase total backscatter rate based on \gls{csi}.
		On the other hand, the optimal input distribution becomes fully deterministic at $\rho=1$ (i.e., best primary performance), where the state maximizes equivalent primary channel \eqref{eq:equivalent_channel} strength is chosen with probability \num{1}.
		In this case, UniScatter node boils down to a \gls{ris} element with $M$ discrete states.
		As $\rho$ moves from \num{0} to \num{1}, the optimal input distribution becomes gradually biased to one state and flexibly balances the primary-backscatter tradeoff.
	\end{subsection}

	\begin{subsection}{Rate Region vs. Input, Beamforming, and Decision Schemes}
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution\label{fi:region_distribution}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_distribution.tex}
				}
			}
			\subfloat[Decision Threshold\label{fi:region_threshold}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_threshold.tex}
				}
			}
			\caption{Average primary-total-backscatter rate regions for different input distribution and decision threshold schemes.}
		\end{figure}
		Fig. \subref*{fi:region_distribution} compares the achievable rate regions by following input designs.
		\begin{itemize}
			% \item ``Exhaustion'' means $K$-dimensional grid search over probability simplex;
			% \item ``\gls{kkt}'' corresponds to Algorithm \ref{al:input_distribution};
			% \item ``Cooperation'' assumes backscatter cooperation/joint encoding at all UniScatters, and employs Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a} to determine \emph{tuple} input distribution;
			\item \textbf{Exhaustion:} $K$-dimensional grid search over probability simplex;
			\item \textbf{\gls{kkt}:} results of Algorithm \ref{al:input_distribution};
					% \item \textbf{Cooperation:} with backscatter cooperation/joint encoding at all UniScatters, Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a} for \emph{tuple} input distribution;
					% \item \textbf{Cooperation:} backscatter cooperation/joint encoding at all UniScatters, \emph{tuple input distribution} by Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a};
					% \item \textbf{Cooperation:} with backscatter cooperation (i.e., joint encoding) at all UniScatters, \emph{tuple input distribution} by Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a};
			\item \textbf{Cooperation:} backscatter cooperation/joint encoding at all UniScatter nodes, tuple input distribution/joint probability array optimization by Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a};
					% with backscatter cooperation (i.e., joint encoding) at all UniScatters, \emph{tuple input distribution} by Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a};
			\item \textbf{Marginalization:} marginal distributions of joint probability array;
			\item \textbf{Decomposition:} normalized tensors of rank-1 \gls{cp} decomposition of joint probability array;
			\item \textbf{Randomization:} Gaussian recovery from joint probability array \cite{Calvo2010}.
		\end{itemize}

		We notice adaptive joint encoding at all nodes provides the outer bound of rate region.
		However, it involves arbitrarily dependent codewords, and backscatter cooperation between passive nodes is generally unaffordable.
		In contrast, the rate region of \gls{kkt} input design in Algorithm \ref{al:input_distribution} approaches that of exhaustive search, and the loss is negligible for $K=2$.
		% Although the randomization method \cite{Calvo2010} achieves similar performance, the computational complexity is much higher as it involves solving $K+1$ linear programming problems
		Although the randomization method \cite{Calvo2010} returns similar rate region, it requires solving $K+1$ linear programming problems before applying Gaussian recovery.
		The marginal distribution is slightly worse than \gls{kkt} despite having the same computational complexity, while the approximation from \gls{cp} decomposition is unsatisfying.

		% TODO: beamforming

		Fig. \subref*{fi:region_threshold} compares the achievable rate region by following threshold schemes.
		\begin{itemize}
			\item \textbf{\gls{dp}:} sequential quantizer grouping by dynamic programming \cite{He2021};
			\item \textbf{\gls{smawk}:} above accelerated by \gls{smawk} algorithm;
			\item \textbf{Bisection:} sequential bisection threshold design \cite{Nguyen2020a};
			\item \textbf{\gls{ml}:} maximum likelihood decision \eqref{eq:detection_threshold_maximum_likelihood} \cite{Qian2019}.
		\end{itemize}

		We observe that input distribution-adaptive threshold designs achieve higher total backscatter rate than \gls{ml}.
		This is because the decision regions can be flexibly adjusted to enhance the capacity of \gls{dmtmac} \eqref{eq:dmtmac}.
		For example, the tuples with negligible input probability should have narrower decision regions than those frequently employed, in order to improve detection performance.
		It emphasizes the importance of joint input distribution and decision region design.

>>>>

		As shown in Fig. \subref*{fi:block_diagram}, UniScatter nodes can be implemented over readily available passive backscatter devices with energy harvester and information decoder.
		Its equivalent circuit and scatter model are presented in Fig. \subref*{fi:equivalent_circuit} and \subref*{fi:scatter_model}.
		When activated by primary transmitter, each node harvests a proportion of the impinging wave for its own operation, decode the embedded coordination information for input distribution control, then applies a potentially random phase shift on the reradiated signal due to backscatter modulation.
		Energy harvesting and information decoding at passive UniScatter nodes can be realized using conventional power-splitting or time-sharing \gls{swipt} protocols \cite{Clerckx2019} or integrated energy-information receiver with pulse position modulated signal \cite{Kim2021a}.
		Besides, relevant \gls{csi} can be acquired using either traditional sequential methods \cite{Bharadia2015,Yang2015b,Guo2019g} or the state-of-the-art parallel approach \cite{Jin2021a}.
		In the following context, we assume perfect primary-backscatter coordination and perfect channel estimation for all links.
		\begin{figure*}[!t]
			\centering
			\subfloat[Block Diagram]{
				\resizebox{0.32\linewidth}{!}{
					\input{assets/illustration/block_diagram.tex}
				}
				\label{fi:block_diagram}
			}
			\subfloat[Equivalent Circuit]{
				\resizebox{0.37\linewidth}{!}{
					\input{assets/illustration/equivalent_circuit.tex}
				}
				\label{fi:equivalent_circuit}
			}
			\subfloat[Scatter Model]{
				\resizebox{0.28\linewidth}{!}{
					\input{assets/illustration/scatter_model.tex}
				}
				\label{fi:scatter_model}
			}
			\caption{
			Block diagram, equivalent circuit, and scatter model of a UniScatter node.
			The solid and dashed vectors represent signal and energy flows.
			The scattering antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.
			}
			\label{fi:uniscatter_node}
		\end{figure*}
	\end{subsection}

@@

			\mathcal{R}_{l} \triangleq [t_{l-1},t_l), \quad 0 \le t_{l-1} \le t_l.

@@

\begin{section}{Rate-Region Characterization}
	To characterize the achievable primary-total-backscatter rate region of the proposed UniScatter system, we aim to maximize the weighted sum mutual information with respect to input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming $\boldsymbol{w}$, and decision thresholds $\boldsymbol{t}$ as
	\begin{maxi!}
		{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{w},\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
		\addConstraint{\boldsymbol{1}^T \boldsymbol{p}_k}{=1,}{\quad \forall k}{\label{co:sum_probability}}
		\addConstraint{\boldsymbol{p}_k}{\ge \boldsymbol{0},}{\quad \forall k}{\label{co:nonnegative_probability}}
		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P}{\label{co:transmit_power}}
		\addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l}{\label{co:sequential_threshold}}
		\addConstraint{\boldsymbol{t}}{\ge \boldsymbol{0}.}{\label{co:nonnegative_threshold}}
	\end{maxi!}
	Since problem \eqref{op:weighted_sum_rate} is highly non-convex, we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$ until convergence.

	\begin{subsection}{Input Distribution}
		For any given $\boldsymbol{w}$ and $\boldsymbol{t}$, we can construct the equivalent \gls{dmtmac} by \eqref{eq:dmtmac} and simplify \eqref{op:weighted_sum_rate} to
		\begin{maxi!}
			{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}}}{I(x_{\mathcal{K}})}{\label{op:input_distribution}}{}
			\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
		\end{maxi!}
		which involves the coupled term $\prod_{k \in \mathcal{K}} P_k(x_{m_k})$ and is non-convex when $K > 1$.
		Following \cite{Rezaeian2004}, we first recast \gls{kkt} conditions of problem \eqref{op:input_distribution} to their equivalent forms, then propose a numerical method that guarantees those conditions on convergence of sequences.
		% ? Next, we propose a numerical method that evaluate the \gls{kkt} input distribution by limit of sequences.
		\begin{remark}
			As demonstrated in \cite{Buhler2011}, \gls{kkt} conditions are generally necessary but insufficient for total rate maximization problems.
			Although \gls{kkt} solutions to problem \eqref{op:input_distribution} may end up being saddle points, we will later show by simulation their average performance can be reasonably close to optimal for a moderate $K$.
			\label{re:input_kkt_distribution}
		\end{remark}
		\begin{proposition}
			The \gls{kkt} optimality conditions for problem \eqref{op:input_distribution} are equivalent to, $\forall k,m_k$,
			\begin{subequations}
				\label{eq:input_kkt_condition}
				\begin{alignat}{2}
					I_k^\star(x_{m_k}) & = I^\star(x_{\mathcal{K}}), \quad   &  & P_k^\star(x_{m_k}) > 0,\label{eq:probable_states} \\
					I_k^\star(x_{m_k}) & \le I^\star(x_{\mathcal{K}}), \quad &  & P_k^\star(x_{m_k}) = 0.\label{eq:dropped_states}
				\end{alignat}
			\end{subequations}
			\label{pr:input_kkt_condition}
		\end{proposition}

@@

	\begin{subsection}{Decision Threshold}
		For any given $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$ and $\boldsymbol{w}$, problem \eqref{op:weighted_sum_rate} reduces to
		\begin{maxi!}
			{\scriptstyle{\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:decision_threshold}}{\label{ob:decision_threshold}}
			\addConstraint{\eqref{co:sequential_threshold},\eqref{co:nonnegative_threshold},}
		\end{maxi!}
		which is still non-convex because variable $\boldsymbol{t}$ appears on the limits of integration \eqref{eq:dmtmac}.
		Fortunately, we can further simplify problem \eqref{op:decision_threshold} as a point-to-point rate-optimal quantizer optimization for a discrete-input continuous-output memoryless channel, thanks to Remark \ref{re:backscatter_decision} and \ref{re:augmented_source}.

@@

		Next, we constrain the feasible domain of problem \eqref{op:decision_threshold} from continuous space $\mathbb{R}_+^{L+1}$ to finite candidate set (i.e., fine-grained discrete energy levels) $\mathcal{T}^{L+1}$.
		\begin{figure}[!t]
			\centering
			\resizebox{0.9\columnwidth}{!}{
				\input{assets/illustration/discrete_outputs.tex}
			}
			\caption{The decision thresholds are selected from fine-grained discrete energy levels instead of continuous space, and each decision region consists of at least one neighbor energy bins.}
			\label{fi:discrete_outputs}
		\end{figure}
		As shown in Fig. \ref{fi:discrete_outputs}, by introducing the extra analog-to-digital conversion step, we can group adjacent high-resolution energy bins for backscatter decision regions.
		Thus, problem \eqref{op:decision_threshold} is recast as
		\begin{maxi!}
			{\scriptstyle{\boldsymbol{t} \in \mathcal{T}^{L+1}}}{I(x_{\mathcal{K}})}{\label{op:decision_threshold_discrete}}{\label{ob:decision_threshold_discrete}}
			\addConstraint{\eqref{co:sequential_threshold},}
		\end{maxi!}
		which can be solved by existing rate-optimal sequential quantizer designs for \gls{dmc}.
		To obtain global optimal solution, \cite{He2021} started from the quadrangle inequality and proposed a \gls{dp} method accelerated by the \gls{smawk} algorithm with computational complexity $\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T})-L)\bigr)$, while \cite{Nguyen2020a} started from the optimality condition for three neighbor thresholds and presented a traverse-then-bisect algorithm with complexity $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$.
		In Section \ref{se:simulation_results}, both schemes will be compared with the \gls{ml} thresholding \cite{Qian2019}
		\begin{equation}
			t_{l}^{\mathrm{\gls{ml}}} = N \frac{\sigma_{l-1}^2 \sigma_{l}^2}{\sigma_{l-1}^2 - \sigma_{l}^2} \log \frac{\sigma_{l-1}^2}{\sigma_{l}^2}, \quad l \in \mathcal{L} \setminus \{L\},
			\label{eq:detection_threshold_maximum_likelihood}
		\end{equation}
		which is generally suboptimal for problem \eqref{op:decision_threshold} except when all nodes are with equiprobable inputs.
	\end{subsection}
\end{section}

\begin{section}{Simulation Results}
	% TODO compare PGD and primary-MRT beamformers
	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision design for the UniScatter system in Fig. \ref{fi:uniscatter_network}.
	We assume the AP-user distance is \qty{10}{\meter}, $K=2$ UniScatter nodes are randomly dropped within a disk of radius \qty{2}{\meter} centered at the user, the \gls{ap} is with $Q=4$ transmit antennas and an average power budget $P=\qty{36}{\dBm}$, the nodes employs \num{4}-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$, and the symbol period ratio is $N=20$.
	For all channels involved, we consider a distance-dependent path loss model
	\begin{equation}
		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma,
	\end{equation}
	together with a Ricean fading model
	\begin{equation}
		\boldsymbol{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\boldsymbol{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\boldsymbol{H}}
	\end{equation}
	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at distance $d_0=\qty{1}{\meter}$, $\kappa$ is the Ricean $K$-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with entries of unit magnitude, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with entries in standard \gls{iid} \gls{cscg} distribution.
	We choose $\gamma_{\mathrm{D}}=2.6$, $\gamma_{\mathrm{F}}=2.4$, $\gamma_{\mathrm{B}}=2$, and $\kappa_{\mathrm{D}}=\kappa_{\mathrm{F}}=\kappa_{\mathrm{B}}=5$ for direct, forward and backward links.
	The finite threshold domain $\mathcal{T}$ comes from $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence level $1-\varepsilon$, where $b=8$ and $\varepsilon=\num{2.22e-16}$.
	All achievable rate curves/regions are averaged over \num{3000} realizations, and the parameters remain fixed unless otherwise specified.

	\begin{subsection}{Input Distribution versus Link Priority}
		\begin{figure}[!t]
			\centering
			\subfloat[Instance 1\label{fi:distribution_weights_1}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/distribution_weights_1.tex}
				}
			}
			\subfloat[Instance 2\label{fi:distribution_weights_2}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/distribution_weights_2.tex}
				}
			}
			\caption{Typical instances of node input distribution under different weights.}
			\label{fi:distribution_weights}
		\end{figure}
		The objective of this study is to demonstrate each UniScatter node can adjust its input distribution based on \gls{csi} and link priority to balance backscatter modulation and passive beamforming.
		For this aim, we evaluate the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution} for a single node under different weights $\rho=\{0,0.1,0.2,0.3,1\}$ in Fig. \ref{fi:distribution_weights}, where \subref*{fi:distribution_weights_1} and \subref*{fi:distribution_weights_2} are two representative instances.
		We observe that as $\rho$ increases from \num{0} to \num{1}, the \gls{kkt} input distribution
		gradually progresses from slightly skewed to completely biased.
		For $\rho=0$ where backscatter performance is absolutely prioritized, the \gls{csi}-adaptive channel coding at the UniScatter node provides higher backscatter rate than conventional \gls{bc} and \gls{sr} nodes with uncoded equiprobable inputs.
		On the other hand, for $\rho=1$ where primary performance is absolutely prioritized, the input probability is \num{1} at the state that maximizes the equivalent primary channel strength, and \num{0} at the others.
		In this case, the reflection pattern over time is fully deterministic, and the UniScatter node indeed boils down to a \gls{ris} element with discrete phase shifts.
		These observations meet our expectation that UniScatter nodes include scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} as special cases, and generalize backscatter modulation and passive beamforming from the perspective of input distribution design.
	\end{subsection}

	\begin{subsection}{Backscatter Rate versus Output Discretization Bit}
		Since the transformation from problem \eqref{op:decision_threshold} to \eqref{op:decision_threshold_discrete} introduces performance degradation, we investigate the impact of threshold domain discretization on the total backscatter rate.

		% TODO Total Backscatter Rate versus Output Discretization Bit
		TODO

	\begin{subsection}{Rate Region under Different Schemes}
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution\label{fi:region_distribution}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_distribution.tex}
				}
			}
			\\
			\subfloat[Active Beamforming\label{fi:region_beamforming}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_beamforming.tex}
				}
			}
			\subfloat[Decision Threshold\label{fi:region_threshold}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_threshold.tex}
				}
			}
			\caption{
				Average primary-total-backscatter rate regions for different input distribution, active beamforming, and decision threshold schemes.
				``BSP'' means backscatter symbol period.
			}
		\end{figure}
		For the \gls{bcd} algorithm considered in the rest of this paper, we choose the \gls{kkt} input distribution by Algorithm \ref{al:input_distribution}, the \gls{pgd} active beamforming by Algorithm \ref{al:active_beamforming}, and the \gls{smawk} decision threshold by \cite{He2021} as reference.
		The impact of different component schemes are explored below.

		\begin{subsubsection}{Input Distribution}
			We compare the following input distribution schemes for problem \eqref{op:input_distribution}:
			\begin{itemize}
				\item \emph{Exhaustion:} Exhaustive grid search over the probability $K$-simplex with resolution $\Delta p = \num{1e-3}$;
				% \item \emph{\gls{kkt}:} Numerical evaluation of the \gls{kkt} solutions by Algorithm \ref{al:input_distribution};
				\item \emph{\gls{kkt}:} Numerical \gls{kkt} solution evaluation by Algorithm \ref{al:input_distribution};
				\item \emph{Cooperation:} Numerical symbol tuple distribution (i.e., $K$-dimensional joint probability array) evaluation by the Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a}.
			\end{itemize}

			Since \emph{Cooperation} involves full transmit cooperation of all nodes, we also propose the following recovery methods from the joint probability array for independent backscatter encoding:
			\begin{itemize}
				\item \emph{Marginalization:} Marginal probability distributions;
				\item \emph{Decomposition:} Normalized rank-\num{1} \gls{cp} decomposition tensors;
				\item \emph{Randomization:} Random search with correlation matrix guidance \cite{Calvo2010}.
			\end{itemize}

			Fig. \subref*{fi:region_distribution} shows the achievable rate regions for those input distribution schemes.
			We observe that \emph{Cooperation} provides the outer bound for all achievable rate regions.
			Although transmit cooperation between UniScatter nodes can be generally helpful, it requires joint encoding with arbitrarily dependent codewords, which introduces extra coordination burden and may be unaffordable for a large $K$.
			We also notice the average performance of \emph{\gls{kkt}} input distribution design by Algorithm \ref{al:input_distribution} is extremely close to that of \emph{Exhaustion}, and the loss is indistinguishable for $K=2$.
			This verified our claim in Remark \ref{re:input_kkt_distribution}.
			Despite \emph{Randomization} yields a similar result, the computational complexity is much higher (loops over $K+1$ linear programming problems) and the performance is backed by numerous random instances.
			In contrast, the low-complexity \emph{Marginalization} returns a comparable result and the rate loss is insignificant when $K$ is small.
			Finally, \emph{Decomposition} suffers from much lower average total backscatter rate, as the rank-\num{1} \gls{cp} approximation can be inaccurate for some channel-drop realizations.
		\end{subsubsection}
